### 2017-03-19 papers.tex
papers.tex: Update ToC heading
And so the bear joke grows labored...
papers.tex: Clear out stale temporary TODOs
papers.tex: Fix breaking typo in Tom7's paper title

% TODO: Update heading
\addproceedings{ToC About Proceedings! Have We Got Papers for You!}

% TODO: Add any new reviews
% TODO: Substitute in new PC message
% TODO: Spellcheck papers list
% TODO: Page numbers fixes?
% TODO: Add ice skating photos?
% TODO: Change title page font

% TODO: Update track "numbering" scheme
\addtrack{Bear track}{Strong Accept}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Joe Doyle}
	{}
	{SIGBOVIK_2017_paper_14}
	{3cm}
	{}
\addpaper
	{I'm on vacation so I'm submitting a vacation picture instead of a paper, or, perhaps, a vacation photo in the format of a paper; I hope a predatory open access journal e-mails me about this article}
	{Jim McCann}
	{}
	{SIGBOVIK_2017_paper_15}
	{0cm}
	{}

@@

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{3cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{1cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{2M\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

>>>>

\addproceedings{These papers are so awesome few can bear to look away!}

% TODO: Add any new reviews
% TODO: Spellcheck papers list
% TODO: Add ice skating photos?
% TODO: Change title page font

\addtrack{Bear track}{Strong Accept}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Joe Doyle}
	{}
	{SIGBOVIK_2017_paper_14}
	{3cm}
	{}
\addpaper
	{I'm on vacation so I'm submitting a vacation picture instead of a paper, or, perhaps, a vacation photo in the format of a paper; I hope a predatory open access journal e-mails me about this article}
	{Jim McCann}
	{}
	{SIGBOVIK_2017_paper_15}
	{0cm}
	{}

@@

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{3cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{1cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{ZM\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}
